When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-09-25 doc/paper/vpd_et_paper.tex
lint collected paper plots and seperated plot functions from script (now in codebase)
seeking easy solution to overlaps

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig01.pdf}
\caption{Plant functional type and location of sites used in analysis.}
\label{map_fig}
 \end{figure}

@@

By construction, the variability in the LAI term (Equation \ref{lai}) contains all model and observational uncertities. LAI also has physical meaning corresponding to ``true'' leaf area, and we expect that it would be approximately $O(1)$. We can have some confidence in our framework, including the assumption of constant uWUE, if calculated LAIs are generally $O(1)$. Figure \ref{lai_fig} presents the histogram of calculated LAIs with outliers (lowest and highest 5\% percent) and unphysical values (LAI $<$ 0.) removed.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig01.pdf}
\caption{Plant functional type and location of sites used in analysis. Note should probably just split this into 4 continents (US, Europe, Africa, Australia).}
\label{map_fig}
 \end{figure}

@@

By construction, the variability in the LAI term (Equation \ref{lai}) contains all model and observational uncertities. LAI also has physical meaning corresponding to ``true'' leaf area, and we expect that it would be approximately $O(1)$. We can have some confidence in our framework, including the assumption of constant uWUE, if calculated LAIs are generally $O(1)$. Figure \ref{lai_fig} presents the histogram of calculated LAIs with outliers (lowest and highest 5\% percent) and unphysical values (LAI $<$ 0.) removed. All remaining LAI values are $O(1)$ which provides confidence in model framework.

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig02.png}
\caption{Histogram of LAI values calculated for each site and time according to Equation \ref{lai}. The lowest and highest 5\% are removed as outliers, as well as any values below 0. The curve is normalized such that its area is 1.}
\label{lai_fig}
 \end{figure}
